PANCHANGE_variable_creation

### 2020-12-17 PANCHANGE_analysis.Rmd
fixed prefer not to say factorising

@@

  ## Row labels
  independent.variables <- c("intercept",
                             explan_var,
                             "Comorbid depression and anxiety",
                             "Depressive disorders",
                             "Anxiety disorders",
                             "Eating disorders",
                             "Obsessive compulsive disorders",
                             "Comorbid psychotic and bipolar disorders",
                             "Psychotic disorders",
                             "Bipolar disorder",
                             "Post traumatic stress disorder",
                             "Autism spectrum disorder",
                             "Attention deficit hyperactivity disorder",
                             "Personality disorders",
                             "Female",
                             "Non-binary/Self-defined",
                             "16-18",
                             "19-25",
                             "36-45",
                             "46-55",
                             "56-65",
                             "66-70",
                             "71-75",
                             "76+",
                             "Mixed or multiple ethnicities",
                             "Asian",
                             "Black",
                             "Other",
                             "Key worker",
                             "Unemployed",
                             "Student",
                             "Retired",
                             "Time between lockdown and baseline")
  ## categories to facet on  
  categories <- c("Intercept",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Gender (Reference male)",
                  "Gender (Reference male)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Other")

  ## Disorder dimension  
  groups <- c(group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group)

@@

  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed_reordered",
                             "Ethnicity_collapsed",
                             "employment_prior_covid",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ ")

@@

gad.prepan.lm <-  lm(formula = gad.sum_score_base.GAD.prepandemic.glmformula,
                            dat.prepan)
gad.retro.lm <- lm(formula = gad.sum_score_base.GAD.retrospective.glmformula,
                            dat.retro)

>>>>

Note: make sure we impute retrospective data for those who did not change their feelings

```{r impute retro for those who did not change}

dat$gad.sum_score_retro <- ifelse(dat$gad.pandemic_felt_feelings == "No different", dat$gad.sum_score_base,dat$gad.sum_score_retro)
dat$phq.sum_score_retro <- ifelse(dat$phq.pandemic_felt_feelings == "No different", dat$phq.sum_score_base,dat$phq.sum_score_retro)

@@

  ## Row labels
  independent.variables <- c("intercept",
                             explan_var,
                             "Comorbid depression and anxiety",
                             "Depressive disorders",
                             "Anxiety disorders",
                             "Eating disorders",
                             "Obsessive compulsive disorders",
                             "Comorbid psychotic and bipolar disorders",
                             "Psychotic disorders",
                             "Bipolar disorder",
                             "Post traumatic stress disorder",
                             "Autism spectrum disorder",
                             "Attention deficit hyperactivity disorder",
                             "Personality disorders",
                             "Did not report or did not know",
                             "Female",
                             "Non-binary/Self-defined",
                             "16-18",
                             "19-25",
                             "36-45",
                             "46-55",
                             "56-65",
                             "66-70",
                             "71-75",
                             "76+",
                             "Mixed or multiple ethnicities",
                             "Asian",
                             "Black",
                             "Other",
                             "Key worker",
                             "Unemployed",
                             "Student",
                             "Retired",
                             "Time between lockdown and baseline")
  ## categories to facet on  
  categories <- c("Intercept",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Gender (Reference male)",
                  "Gender (Reference male)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Other")

  ## Disorder dimension  
  groups <- c(group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group)

@@

  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "DidNotRespondMHD",
                             "Gender_collapsed",
                             "age_category_collapsed_reordered",
                             "Ethnicity_collapsed",
                             "employment_prior_covid",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ ")

@@

gad.prepan.lm <-  lm(formula = gad.sum_score_base.GAD.prepandemic.glmformula,
                            dat.prepan)

gad.retro.lm <- lm(formula = gad.sum_score_base.GAD.retrospective.glmformula,
                            dat.retro)

### 2020-12-17 PANCHANGE_variable_creation.Rmd
fixed prefer not to say factorising

dat <- dat %>%
  mutate(DidNotRespondMHD  = 
           case_when(
             (is.na(depressive_disorders) &
 is.na(anxiety_disorders) &
  is.na(eating_disorders) &
  is.na(obsessive_compulsive_disorders) &
 is.na(psychotic_disorders) &
  is.na(mhd.mania_hypomania_bipolar_or_manicdepression) &
  is.na(mhd.posttraumatic_stress_disorder_ptsd) &    
  is.na(autism_spectrum_disorder) &
  is.na(mhd.attention_deficit_hyperactivity_disorder) &
  is.na(mhd.personality_disorder) &
  is.na(control)) ~ 1))

>>>>

dat <- dat %>%
  mutate(DidNotRespondMHD  = 
           case_when(
             (is.na(depressive_disorders) &
 is.na(anxiety_disorders) &
  is.na(eating_disorders) &
  is.na(obsessive_compulsive_disorders) &
 is.na(psychotic_disorders) &
  is.na(mhd.mania_hypomania_bipolar_or_manicdepression) &
  is.na(mhd.posttraumatic_stress_disorder_ptsd) &    
  is.na(autism_spectrum_disorder) &
  is.na(mhd.attention_deficit_hyperactivity_disorder) &
  is.na(mhd.personality_disorder) &
  is.na(control)) ~ "Prefer not to say", 
 TRUE ~ "Responded to MHD"))

dat <- dat %>%
  mutate(DidNotRespondMHD = recode_factor(DidNotRespondMHD, 
                "Prefer not to say" ="Prefer not to say",
                "Responded to MHD" ="Responded to MHD"))
